Image Forensics using Reflections on Curved Surfaces

### 2014-02-27 paper/main.tex
minor paper edits

One possible alternative to looking at the minimum distance to the center would be to consider the the point of intersection of all the rays, similar to the vanishing point method in the planar case. However, the spherical case is much more sensitive to error than the planar case. In the planar case the incident rays are parallel, so their vanishing point often lies far outside the image, and so the position of the intersection point is not very sensitive to a difference of a few pixels in the points picked. In the spherical case, however, it is not uncommon for the projections of the incident rays to not intersect cleanly even in genuine images.

@@

One strength of both this test and almost any consistency test is that it should not produce any false positives in theory, as long as the tolerance for genuine images is calibrated correctly. It may miss some false negatives, in the case of an object moving towards or away from the sphere, but any drastic offset from the center is clearly a forgery.

@@

It is easy to envision that a forger could beat these techniques by performing the same tests and adjusting as needed. If they were to splice in an object and its reflection, they could align and scale them such that the projections of the incident rays go through the center of the sphere. This is limited mostly by the fact that in a real world scenario, the forger would be restricted by how the reflective surface in the source image is set up. Nonetheless, more research into counterforensics is recommended.

>>>>

One possible alternative to looking at the minimum distance to the center would be to consider the the point of intersection of all the rays, similar to the vanishing point method in the planar case. However, the spherical case is much more sensitive to error than the planar case. In the planar case the incident rays are parallel, so the angle between their projections tends to be very small, and so the position of the intersection point is not very sensitive to a difference of a few pixels in the points picked. In the spherical case, however, it is not uncommon for the projections of the incident rays to not intersect cleanly even in genuine images.

@@

One strength of both this test and almost any consistency test is that it should not produce any false positives in theory, as long as the tolerance for genuine images is calibrated correctly. It may produce some false negatives, in the case of an object moving towards or away from the sphere, but any drastic offset from the center is clearly a forgery.

@@

It is easy to envision that forgers could beat these techniques by performing the same tests and adjusting as needed. If they were to splice in an object and its reflection, they could align and scale them such that the projections of the incident rays go through the center of the sphere. This is limited mostly by the fact that in a real world scenario, the forger would be restricted by how the reflective surface in the source image is set up. Nonetheless, more research into counterforensics is recommended.
